Making Sequential Programs Deterministic

### 2019-04-05 related.tex

\cite{LuoHEM2014} study 51 open source projects and analyze the most common root causes of
test flakiness. The findings in the paper suggest that most of the flakiness in tests is caused by
the use of async await, concurrency, or due to test order dependency.~\cite{Plotkin:1993:LPP:645891.671433}
perform an empirical study on open source benchmarks that concur with the results of~\cite{LuoHEM2014}.
Additionally, the authors of this paper study the effects of removing these test smells. Their results suggest that
refactoring the test code smells fixed more than half of the identified flaky tests.

@@

Failing tests that are unrelated to code changes can be expensive both in terms of monetary costs and
developer effort. \cite{Herzig:2015:EDF:2819009.2819018} propose techniques to classify tests as false alarms
if they are known to be caused by testing infrastructure or other environment issues.~\cite{Huo:2014:IOQ:2635868.2635917}
propose an approach that detects brittle assertions in tests by performing a taint analysis on inputs classified as 
controlled and uncontrolled.~\cite{ZhangJWMLEN2014} investigate the effects of test independence assumption
on other techniques such as test prioritization, selection, etc. 
\cite{BellKMD2015}
\cite{Gyori:2015:RTD:2771783.2771793}
\cite{Dan:2013:10.1007/978-3-642-39038-8_25}
\cite{Vahabzadeh:2015:7332456}
\cite{Fowler}
\cite{Sudarshan}

\todo{A NonDet annotation:
  \url{http://www.swi-prolog.org/pldoc/man?section=modes}}

>>>>

Nondeterminism in tests is of interest to both
researchers and software developers alike~\cite{Fowler,Sudarshan}.
\cite{LuoHEM2014} study 51 open source projects and analyze the most common root causes of
test flakiness. The findings in the paper suggest that most of the flakiness in tests is caused by
the use of async await, concurrency, or due to test order dependency.~\cite{Plotkin:1993:LPP:645891.671433}
perform an empirical study on open source benchmarks that concur with the results of~\cite{LuoHEM2014}.
Additionally, the authors of this paper study the effects of removing these test smells. Their results suggest that
refactoring the test code smells fixed more than half of the identified flaky tests.

@@

Failing tests that are unrelated to code changes can be expensive both in terms of monetary costs and
developer effort. \cite{Herzig:2015:EDF:2819009.2819018} propose techniques to classify tests as false alarms
if they are known to be caused by testing infrastructure or other environment issues.~\cite{Huo:2014:IOQ:2635868.2635917}
propose an approach that detects brittle assertions in tests by performing a taint analysis on inputs classified as 
controlled and uncontrolled.~\cite{ZhangJWMLEN2014} investigate the effects of test independence assumption
on other techniques such as test prioritization, selection, etc. Other approaches~\cite{BellKMD2015,Gyori:2015:RTD:2771783.2771793}
analyze test dependencies and either prevent them or use this information for other optimizations.
\cite{Dan:2013:10.1007/978-3-642-39038-8_25,Vahabzadeh:2015:7332456} focus on differentiating bugs due to tests
from those caused by source code.

%\todo{A NonDet annotation:
%  \url{http://www.swi-prolog.org/pldoc/man?section=modes}}
